\makeatletter
\def\input@path{{../macros/}{../../macros/}}
\makeatother


\documentclass[a4paper]{article}

\usepackage{mydoc}
\input{mydoc.tex}
\usepackage{easytable}

\title{The package \package{easytable}}

\begin{document}
\maketitle
\begin{abstract}
  The \package{easytable} package is a macro package for writing
  tables, with equal column widths or equal rows heights or both, with
  various kinds of rules~(lines) between rows and columns.  It uses an
  array/tabular-like syntax.
\end{abstract}

\pagestyle{fpage}
\def\sectionmark#1{\markboth{The package \package{easybmat}}{The package \package{easybmat}}}
\let\chaptermark\sectionmark
\let\subsectionmark\sectionmark

\section{How to use it}
Load the package in the usual way:
\begin{verbatim}
  \documentclass{article}
  .
  .
  \usepackage[thinlines,thiklines]{easytab}
  .
  .
\end{verbatim}
The options \texttt{thinlines}, and \texttt{thiklines} are self explanatory.

The package \package{easytab} provides the \envname{TAB} environment
which is a simple (re)\-implementation of the array---tabular environment,
with some limitation and some additional features.  The syntax is
\begin{verbatim}
  \begin{TAB}`(eq)'`[ex]'`{cc...c}'`{cc...c}'
     a & b & ... & n \\
     ...
  \end{TAB}
\end{verbatim}
or 
\begin{verbatim}
  \begin{TAB}`(eq,mx,my)'`[ex,MX,MY]'`{cc...c}'`{cc...c}'
     a & b & ... & n \\
     ...
  \end{TAB}
\end{verbatim}
%
\begin{dotlist}
  \item
  \verb'(eq)' or \verb'(eq,mx,my)'.  By \verb'eq' you can balance
  the rows or the column or both, as shown in this table:
  \begin{center}
    \textbf{Table 1.}\nobreak\\[1em]
    \begin{tabular}{|l|l|}
      \hline
      value of \verb|eq| & effect \\
      \hline
      \verb'@' & no balancing \\
      \verb'r' & equal rows heights \\
      \verb'c' & equal column widths  \\
      \verb'b' & equal rows heights and equal column widths \\
      \verb'e' & equal rows heights and column widths \\
      \hline
    \end{tabular}
  \end{center}
  By \verb'mx' and \verb'my' you can modify the minimum size of the
  box in the TAB environment.  This must be a valid measure e.g. 2pt. 
  This is useful in writing matrices an vectors.
  %%
  \item
  \verb'[ex]' or \verb'[ex,MX,MY]'.  By ``\verb'ex''' you can specify
  the amount of extra space around the item in the \envname{TAB}
  environment.  The default is \verb'2pt'.  By \verb'MX' and \verb'MY'
  you can modify the minimum size of the whole table in the TAB
  environment.  This must be a valid measure e.g.~10cm.
  %%  
  \item
  The first ``\verb'{cc...c}''' is the definition of the columns and
  their alignment.  The possible alignment for the columns are:
  \begin{center}
    \textbf{Table 2.} \nobreak\\[1em]
    \begin{tabular}{|l|l|}
      \hline
      \verb'c' & centering \\
      \verb'l' & flush left \\
      \verb'r' & flush right \\
      \hline
    \end{tabular}
  \end{center}
  %%
  \item
  The second ``\verb'{cc...c}''' is the definition of the rows their
  alignment.  The possible alignment for the rows are:
  \begin{center}
    \textbf{Table 3.} \\[1em]
    \begin{tabular}{|l|l|}
      \hline
      \verb'c' & centering \\
      \verb't' & flush top \\
      \verb'b' & flush bottom \\
      \hline
    \end{tabular}
  \end{center}
\end{dotlist}
\textbf{IMPORTANT:} The package can manage matrices with a maximum 
of \verb|30| rows by \verb|30| columns.\\
%
\textbf{IMPORTANT:} The functionality of the environment ``TAB'' is 
the same of the environment ``BMAT'' the only difference is that its 
entries are in ``text'' mode not in ``mathematic'' mode. Please read 
the documentation of the package \package{easybmat} to understand
how to use ``TAB''.

\end{document}
